---
title: "Building models for advertisement campaigns"
---
set data path:
```{r cache=TRUE}
path <- "/home/witek/projects/ml/campaign-predictor-r/"
setwd(path) 
```

Read data
```{r cache=TRUE}
r1 <- read.csv("r1.csv", header = TRUE)
r2 <- read.csv("r2.csv", header = TRUE)
r3 <- read.csv("r3.csv", header = TRUE)
r4 <- read.csv("r4.csv", header = TRUE)
r5 <- read.csv("r5.csv", header = TRUE)
r6 <- read.csv("r6.csv", header = TRUE)
r7 <- read.csv("r7.csv", header = TRUE)
r8 <- read.csv("r8.csv", header = TRUE)
r9 <- read.csv("r9.csv", header = TRUE)
r10 <- read.csv("r10.csv", header = TRUE)
r11 <- read.csv("r11.csv", header = TRUE)
r12 <- read.csv("r12.csv", header = TRUE)
```

Remove empty column:
```{r cache=TRUE}
r1<-r1[,-14]
r2<-r2[,-14]
r3<-r3[,-14]
r4<-r4[,-14]
r5<-r5[,-14]
r6<-r6[,-14]
r7<-r7[,-14]
r8<-r8[,-14]
r9<-r9[,-14]
r10<-r10[,-14]
r11<-r11[,-14]
r12<-r12[,-14]
```

Add id column:
```{r cache =TRUE}
r1[, "ad_id"] <- rep(1, nrow(r1))
r2[, "ad_id"] <- rep(2, nrow(r2))
r3[, "ad_id"] <- rep(3, nrow(r3))
r4[, "ad_id"] <- rep(4, nrow(r4))
r5[, "ad_id"] <- rep(5, nrow(r5))
r6[, "ad_id"] <- rep(6, nrow(r6))
r7[, "ad_id"] <- rep(7, nrow(r7))
r8[, "ad_id"] <- rep(8, nrow(r8))
r9[, "ad_id"] <- rep(9, nrow(r9))
r10[, "ad_id"] <- rep(10, nrow(r10))
r11[, "ad_id"] <- rep(11, nrow(r11))
r12[, "ad_id"] <- rep(12, nrow(r12))
```

Combine datasets:
```{r cache=TRUE}
dane <- rbind(r1,r2)
dane <- rbind(dane, r3)
dane <- rbind(dane, r4)
dane <- rbind(dane, r5)
dane <- rbind(dane, r6)
dane <- rbind(dane, r7)
dane <- rbind(dane, r8)
dane <- rbind(dane, r9)
dane <- rbind(dane, r10)
dane <- rbind(dane, r11)
dane <- rbind(dane, r12)
```
Save data
```{r cache=TRUE}
saveRDS(dane, file = "dane.rda")
```

Why can't se use the build in randomForest function?

```{r cache=TRUE, error=TRUE}
require("randomForest")
model<-randomForest(wynik~.,r1, na.action = na.omit )
```
Some of the categories have more then 52 levels; randomForest function can't handle them<br>
Most of standard functions/tools have this limitation; use one-hot or build forest manually<br>
example:

```{r cache=TRUE,error=TRUE}
require("rpart")
model<-rpart(wynik~.,r1)
```


Process:
1. Build M trees using rpart<br>
2. Classification usign M trees. Each of the trees returns yes and no probability. Average "yes" probabilities
3. Executed for 12 campaings (12 probabilities of an optin)
<br>

Single campaign procedure: <br>
input:<br>
data<br>
M - number of trees <br>
n - number of observations <br>
output: <br>
models - vektor of M tree models
```{r cache=TRUE}
build_forest<- function(data, M=500, n = 35){

  models<- vector(mode = "list", length = M)
  pos_index<- which(data$wynik=="tak")
  neg_index<- which(data$wynik=="nie")
  for(i in 1:M){
    
    learningset_pos<- sample(pos_index, n, replace = TRUE)
    learningset_neg<- sample(neg_index, n, replace = TRUE)
    learningset<- rbind(data[learningset_pos,],data[learningset_neg,])
    
    models[[i]]<-rpart(wynik~plec+miasto_kat+wojewodztwo+domena_kat+wiek+
                         typ_adresu+poczta,data = learningset, control = rpart.control(maxdepth = 20))
    
  }
  return(models)
}

```

Classification function:<br>
input: <br>
obs - obesrvations <br>
allmodels - vactor from function *build_forest*
output: <br>
p_tak - vector of "yes" responses
```{r cache=TRUE}
classify_observations<- function(obs, allmodels){
  
  p_tak = numeric(length(allmodels))
  
  for(i in 1:length(allmodels)){
    tak = 0
    for(j in 1:length(allmodels[[i]])){
      
      attr<-attr(allmodels[[i]][[j]], "xlevels")
      for(nazwa in names(attr)){
        
        if(!(obs[,nazwa]%in%attr[[nazwa]])){
          obs[,nazwa] = as.factor(NA)
        }
      }
      tak = tak + predict(allmodels[[i]][[j]] ,obs)[,"tak"]
    }
    p_tak[i]= tak/(length(allmodels[[i]]))
  }
  return(p_tak)
}
```
<br>
<br><br>
output: <br>
result_table - confusion matrix
```{r cache=TRUE}
require("stringr")
testuj<- function(M = 500,n = 35, neg_test = 1000, allmodelsRDS = "allmodels.rda", 
                  testowyRDS = "testowy.rda", predykcjeRDS = "predykcje.rda",
                  logRDS = "log.rda"){
  allmodels<- vector(mode = "list", length = 12)
  reklamy<-c("r1","r2","r3","r4","r5","r6","r7","r8","r9","r10","r11","r12")
  testowy<- data.frame("id" = c(), "plec"=c(),"miasto_kat"=c(), "wojewodztwo"= c(),
                       "domena_kat"= c(), "wiek"= c(),"IPA"= c(), "IPB" = c() ,
                       "wynik" = c(), "typ_adresu" = c(), "wybory" = c(), 
                       "poczta" = c(), "data" = c(), "ad_id" = c())
  
  for(i in 1:length(allmodels)){
    testowy_neg<- sample(which(get(reklamy[i])$wynik=="nie"), neg_test)
    testowy<- rbind(testowy, get(reklamy[i])[testowy_neg,])
    allmodels[[i]]<-build_forest(get(reklamy[i])[-testowy_neg,],M=M,n )
    saveRDS(allmodels, file = allmodelsRDS)
    saveRDS(testowy, file = testowyRDS)
    saveRDS((sort( sapply(ls(),function(x){object.size(get(x))}))),file = logRDS)
  }
  predykcje<- numeric(nrow(testowy))
  for(i in 1:nrow(testowy)){
    
    predykcje[i]<- which.max(classify_observations(testowy[i,], allmodels))
    saveRDS(predykcje, file = predykcjeRDS)
    saveRDS((sort( sapply(ls(),function(x){object.size(get(x))}))),file = logRDS)
    
  }
  result_table <- table(predykcje,testowy$ad_id)
  return(result_table)
}

```
Function testing two models<br>
<br>
input:<br>
k1file - model 1<br>
k2file - model 2<br>
pred1file - predictions<br>
pred2file - predictions<br>
testowyfile - test data <br>
n_poz - number of "yes" observations to be used<br>
n_neq - number of "yes" observations to be used<br>
daneRDS - data
<br>
Notes:<br>
testuj_3() won't be executed because it'd take too long
```{r cache=TRUE}
testuj_3<-function(k1file = "am2.rda", k2file = "am2_1.rda", pred1file = "pred1.rda",
                   pred2file = "pred2.rda", testowyfile = "testowy.rda",
                   n_poz = 1000, n_neq = 2000, daneRDS = "dane.rda"){
  
  require("rpart")
  dane <- readRDS(file = daneRDS)
  testowy<- rbind(dane[sample(which(dane$wynik=="nie"),n_poz),],
                   dane[sample(which(dane$wynik=="tak"),n_poz),])
  pred1<- numeric(length(testowy[,1]))
  pred2<- numeric(length(testowy[,1]))
  
  saveRDS(testowy, file = testowyfile)
  
  rm(dane)
  
  k1<- readRDS(file = k1file)
  k2<- readRDS(file = k2file)
  
  for(i in 1:length(pred1)){
    
    pred1[i]<- which.max(classify_observations(testowy[i,],k1))
    pred2[i]<- which.max(classify_observations(testowy[i,],k2))
    saveRDS(pred1, file = pred1file)
    saveRDS(pred2, file = pred2file)
  }
}
```



**am4.rda** <- model consisting of 50 trees for every campaign using 35 yes and 35 no observations
for independent variables : "plec","miasto_kat","wojewodztwo",  "domena_kat", "wiek", "typ_adresu"i "poczta" <br><br>
**am4_1.rda** 50 trees 35/35 for all variables
**am3.rda** <- 100 trees 35/35 for : "plec","miasto_kat","wojewodztwo",  "domena_kat", "wiek", "typ_adresu"i "poczta" <br><br>
**am3_1.rda** <- 100 trees 35/35 for all <br><br>
**am2.rda** <- 200 trees 35/35 for: "plec","miasto_kat","wojewodztwo",  "domena_kat", "wiek", "typ_adresu"i "poczta" <br><br>
**am2_1.rda** <- 200 trees 35/35 for all <br><br>



**Example** <br>
Read model
```{r cache=TRUE}
am3<- readRDS(file = "am3.rda")
```
Select observation<br>
Results<br>
Vector of probabilities for the slected observation for avery of the 12 campaigns
```{r cache=TRUE}
r4[1024,]
ptm <- proc.time()
classify_observations(r4[1024,], am3)
proc.time() - ptm
```

</br></br><br>

For random observation:
```{r cache=TRUE}
i<-sample(nrow(dane),1)
dane[i,] 
classify_observations(dane[i,], am3)
```
For random "yes":
```{r cache=TRUE}
i<-sample(which(dane$wynik=="tak"),1)
dane[i,]
classify_observations(dane[i,], am3)
```
For random "no":
```{r cache=TRUE}
i<-sample(which(dane$wynik=="nie"),1)
dane[i,]
classify_observations(dane[i,], am3)
```
**Example tests**<br><br>
<br><br>
**am4**. Confusion martix: rows = predictions; columns = actual
```{r cache=TRUE}
testowy4<-readRDS(file = "testowy4.rda")
pred1am4<- readRDS(file = "pred1am4.rda")
pred2am4_1<- readRDS(file = "pred2am4_1.rda")
indeks<-which(testowy4$wynik=="nie")
tabela<-table(pred1am4[indeks], testowy4[indeks,"ad_id"])
tabela

```
Percentages of users who would see a different campaign:
```{r cache=TRUE}
1-sum(diag(tabela))/sum(tabela)
```

**am4_1**
```{r cache=TRUE}
tabela<-table(pred2am4_1[indeks], testowy4[indeks,"ad_id"])
tabela
```

Percentages of users who would see a different campaign:
```{r cache=TRUE}
1-sum(diag(tabela))/sum(tabela)
```

**am3**
```{r cache=TRUE}
testowy3<-readRDS(file = "testowy3.rda")
pred1am3<- readRDS(file = "pred1am3.rda")
pred2am3_1<- readRDS(file = "pred2am3_1.rda")
indeks<-which(testowy3$wynik=="nie")
tabela<-table(pred1am3[indeks], testowy3[indeks,"ad_id"])
tabela

```
Percentages of users who would see a different campaign:
```{r cache=TRUE}
1-sum(diag(tabela))/sum(tabela)
```

**am3_1**
```{r cache=TRUE}
tabela<-table(pred2am3_1[indeks], testowy3[indeks,"ad_id"])
tabela
```

Percentages of users who would see a different campaign:
```{r cache=TRUE}
1-sum(diag(tabela))/sum(tabela)
```

